### 2023-09-17 tcc/introduction.tex
work on - report and tcc

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Chapter 1 -- Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}\label{chp:introduction}
\thispagestyle{headings}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Motivation to study heavy-ion physics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Physics motivation}

\hspace{0.635cm}One motivation to study physics is to understand the
fundamental laws of nature that rule the universe around us. For a long time,
the fundamental questions about nature were the inspiration for mankind
to keep looking for answers. One basic question of physics is 
``\textit{what are the basic building blocks of matter?}'' - how far have we advanced
in this question? According to our current knowledge:\newline

\parbox{0.9\textwidth}{\raggedright\textit{``Particle physics is at the heart of our 
understanding of the laws of nature. It is concerned with the fundamental 
constituents of the Universe, the elementary particles, and the interactions 
between them, the forces. Our current understanding is embodied in the Standard 
Model of particle physics, which provides a unified picture where the forces 
between particles are themselves described by the exchange of particles. 
Remarkably, the Standard Model provides a successful description of all current 
experimental data and represents one of the triumphs of modern physics.''} 
\textbf{Modern Particle Physics, Mark Thomson} \textnormal{\cite{thomson2013modern}}. 
} 
\newline