### 2025-08-02 IFs/banco_questoes_fisica/qs3.tex

\section{\large \textcolor{blue}{Oscilações e ondas}}

\begin{flushleft}
\textbf{\textcolor{blue}{\Large Quest\~ao - }}\\
\noindent

\subsection{Quest\~ao }

\begin{itemize}
\item[(A)] 
\item[(B)] 
\item[(C)]
\item[(D)] 
\item[(E)] 
\end{itemize}

\vspace{0.5cm}

\textcolor{red}{\textbf{Solução:}}\\

A resposta correta é alternativa \colorbox{green!50}{\textbf{...}}.

\end{flushleft}